Reasonably Programmable Literal Notation

### 2018-06-18 icfp18/syntax-icfp18.tex
edits to 2.1.2

\subsubsection{Expansion Typing}
Having found the definition of the \li{$regex} TLM, the client can immediately determine the type of the expansion being generated at each application site because it is specified explicitly by the clause \li{at Regex.t} on Line~2 of Fig.~\ref{fig:regex-tlm-def}. The expansion type of a TLM is analogous to the return type of a function. The identity of \li{Regex.t} is determined relative to the TLM definition site, not at each application site, so the module \li{Regex} need not be in scope at the application site, or it can have been shadowed by a different module. % In Reason, TLM definitions can refer to exactly those modules that a Reason module at the top level of the defining package would have access to, i.e. other top-level modules in the package as well as modules exported by other packages that have been imported by the build system.

>>>>

\subsubsection{Expansion Typing}
Having found the definition of the \li{$regex} TLM, the client can immediately determine the type of the expansion being generated at each application site because it is specified explicitly by the clause \li{at Regex.t} on Line~2 of Fig.~\ref{fig:regex-tlm-def}. The expansion type of a TLM is analogous to the return type of a function. The identity of \li{Regex.t} is determined relative to the TLM definition site, not at the application site, so the module \li{Regex} need not be in scope at the application site, or it can have been shadowed by a different module. % In Reason, TLM definitions can refer to exactly those modules that a Reason module at the top level of the defining package would have access to, i.e. other top-level modules in the package as well as modules exported by other packages that have been imported by the build system.
